Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-04 article.tex
make figures in 'p_bind_per_hydrophobicity'

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Relation between hydrophobicity, TMH and MHC binding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/binds_mhc1_vs_binds_mhc2.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:binds_mhc1_vs_binds_mhc2}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_binds_mhc1.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:hydrophobicity_vs_binds_mhc1}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_binds_mhc2.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:hydrophobicity_vs_binds_mhc2}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/hydrophobicity_vs_is_tmh.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:hydrophobicity_vs_is_tmh}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/is_tmh_vs_binds_mhc1.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:is_tmh_vs_binds_mhc1}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=0.9\textwidth]{p_bind_per_hydrophobicity/is_tmh_vs_binds_mhc2.png}
  \caption{
    \richel{Used simulated data}
  }
  \label{fig:is_tmh_vs_binds_mhc2}
\end{figure}
